Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2024-04-04 article.tex
Mention dataclass

Poincare is a package to define and simulate dynamical systems.
It provides a \texttt{System} class,
where one can define
\texttt{Constant}s; which can be numbers or refer to other constants;
\texttt{Parameter}s, which can be numbers or time-dependent expressions;
\texttt{Variable}s, which represent the state of the system and must be provided with an initial condition;
and create equations linking a variable's derivative with an expression (Figure~\ref{fig-first-order}).
It also allows to define higher-order systems
by assigning an initial condition to a \texttt{Derivative} (Figure~\ref{fig-second-order}).

Within the constraints imposed by Python's current typing and static analyzers,
we define models utilizing Python classes
such that we can benefit from \acp{IDE}' autocomplete and refactoring capabilities.
This design offer several advantages:

>>>>

Poincare is a package to define and simulate dynamical systems.
Based on Python inmutable dataclasses,
it provides a \texttt{System} class,
where one can define
\texttt{Constant}s; which can be numbers or refer to other constants;
\texttt{Parameter}s, which can be numbers or time-dependent expressions;
\texttt{Variable}s, which represent the state of the system and must be provided with an initial condition;
and create equations linking a variable's derivative with an expression (Figure~\ref{fig-first-order}).
It also allows to define higher-order systems
by assigning an initial condition to a \texttt{Derivative} (Figure~\ref{fig-second-order}).

Within the constraints imposed by Python's current typing and static analyzers,
we define models utilizing Python (data)classes
such that we can benefit from \acp{IDE}' autocomplete and refactoring capabilities.
This design offer several advantages:
